Social Computing Article\thanks{This title is temporary}

### 2013-01-15 Article.tex
arrumei umas coisinhas e atualizei os gráficos

\subsubsection{Unique Missing Candidate}

This technique marks a {\em Sudoku} cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block.

\subsubsection{Naked Singles}

This rule marks a {\em Sudoku} cell with value $v$ only if $v$ is the single possible value to mark that cell. The other values must have been eliminated through a process of verifying that they are all present in the span encompassing the cell's row, column and $3 \times 3$ block.

\subsubsection{Hidden Singles}

This rule is similar to the {\em naked singles} rule. It is able to mark cells with more than one candidate value by looking for cells that are the only ones in their row, column or $3 \times 3$ block that can hold a particular value.

\subsubsection{Two out of Three}

@@

\subsubsection{Naked Twins}

>>>>

\subsubsection{Two out of Three Rule}

@@
